---
title: "Statistical Inference Course Project 1"
author: "RossAW"
date: "27 September 2015"
output: pdf_document
---

##Overview

This project consists of two parts, a simulation exercise and a basic inferential data analysis.

```{r}
library(ggplot2)
```
#Simulations

###The Exponential Distribution

The Exponential Distribution is given by



Lets have a look at what that looks like.

```{r}

set.seed(1)
lambda <- 0.2 

NumberOfSims <- 10000 

exponentialRandoms<-rexp(NumberOfSims,lambda)

plot(exponentialRandoms, pch=20, col=rgb(0,0,1,0.2), 
     main = "10,000 observations of the \nexponential 
     distribution with lambda = 0.2",
     ylab= "Exponential Randoms")

hist(exponentialRandoms)

```

 

To answer the remaining questions we need to take the average of 40 random exponentials, 1000 times. This will give us 1000 averages of exponential Randoms.
```{r}
n <- 40 # Average of n random exponentials
AveragOfExponentialRandoms<-NULL

for(i in 1:1000){
    
    AveragOfExponentialRandoms=c(AveragOfExponentialRandoms,mean(rexp(n,0.2)))
}


```

###Sample Mean vs Theoretical Mean 
This compares the mean of the sample means to the theoretical mean.
```{r}

TheoreticalMean<-1/lambda
TheoreticalMean
SampleMean<-mean(AveragOfExponentialRandoms)
SampleMean

```

As predicted by the CLT the mean of the sample means is near identical to the population mean.

###Sample Variance vs Theoretical Variance
This compares the sample varianace to the theoretical variance.
```{r}
SampleVariance<-var(AveragOfExponentialRandoms)
SampleVariance

TheoreticalVariance<-(1/lambda^2)/n
TheoreticalVariance

```

As predicted by the CLT the sample varaiance is near identical to the population variance.

###Distribution vs Normal Distribution
The CLT states that the average of a set of random samples is approximately Normally distributed with a mean given by the propluation mean and a variance given by the standard error of the mean N(mu,sig^2/n)
```{r}
AveragOfExponentialRandoms<-data.frame(AveragOfExponentialRandoms)
TheoreticalSD<-sqrt(TheoreticalVariance)

g <- ggplot(AveragOfExponentialRandoms, aes(x = AveragOfExponentialRandoms)) +
    geom_histogram(binwidth=.3, colour = "black", aes(y = ..density..)) 

g <- g + stat_function(fun = dnorm, size = 2,colour="blue",
                       args = list(mean = TheoreticalMean, sd = TheoreticalSD))

g<-g+ylab("Number of Injuries")+
        xlab("Type of Weather Event")+
        theme(axis.text.x = element_text(angle = 45,hjust = 1))+
        ggtitle("Comparing the Count of Random Exponential Averages \n 
                with the Normal distribution")
g

```


The above graph shows that the distribution is very well described by the normal distribution.
