---
title: "Statistical Inference Course Project Part 2"
author: "RossAW"
date: "27 September 2015"
output: pdf_document
---

In the second portion of the class, we're going to analyze the ToothGrowth data in the R datasets package.

###Loading the Data and Providing a basic summary
```{r}
library(datasets)
library(dplyr)
library(ggplot2)

TGData<-ToothGrowth
SummarisedData<-summarise(group_by(TGData,supp,dose),
                     MeanLen = mean(len,na.rm = TRUE))


ggplot(SummarisedData, aes(x=dose, y=MeanLen, group = supp, colour = supp)) +
    geom_line() +
    geom_point( size=4, shape=21, fill="white")+
    ylab("Mean Tooth Length")+
    xlab("Dose (mg/day)")+
    ggtitle("Mean Tooth Length vs Dose")

summary(TGData)
```

###Use confidence intervals and hypothesis tests to compare tooth growth by supp and dose. (Use the techniques from class even if there’s other approaches worth considering)
```{r}
supp.t1 <- t.test(len~supp, paired=F, var.equal=T, data=TGData)
supp.t2 <- t.test(len~supp, paired=F, var.equal=F, data=TGData)


supp.result <- data.frame("p-value"=c(supp.t1$p.value, supp.t2$p.value),
                          "Conf-Low"=c(supp.t1$conf[1],supp.t2$conf[1]),
                          "Conf-High"=c(supp.t1$conf[2],supp.t2$conf[2]),
                          row.names=c("Equal Var","Unequal Var"))
supp.result
```

###State your conclusions and the assumptions needed for your conclusions.

We can concluded that both orange juice and vitamin C have an impact on tooth growth. We can also concluded that increasing the dosage will increase the impact on tooth growth ove the 0.5 to 2mg/day range.